R Notebook

### 2017-06-23 doc/RMD/data-comparison.Rmd
update repeat length parsing in data comparison

First we need to transform the data to something that

```{r}
dat <- saj %>% 
  select(-(Isolate:Host)) %>% 
  df2genind(ind.names = saj$Isolate, 
            strata = select(saj, MCG:Host), # Filtering out severity and Isolate
            ploidy = 1) %>%
  as.genclone()
nameStrata(dat)[2] <- "Region"
pops <- levels(strata(dat)$Region)
levels(strata(dat)$Region) <- case_when(pops == "FR" ~ "France", 
                                        pops == "MX" ~ "Mexico", 
                                        pops == "AU" ~ "Australia", 
                                        TRUE ~ pops)
dat
locNames(dat)

repeat_lengths <-
  c(
  `5-2(F)` = 2.000000,
  `5-3(F)` = 0.500000,
  `6-2(F)` = 6.000000,
  `7-2(F)` = 2.000000,
  `8-3(H)` = 2.000000,
  `9-2(F)` = 2.000000,
  `12-2(H)` = 2.000000,
  `17-3(H)` = 3.000000,
  `20-3(F)` = 2.000000,
  `36-4(F)` = 0.500000,
  `50-4(F)` = 0.500000,
  `55-4(F)` = 4.000000,
  `92-4(F)` = 2.000000,
  `106-4(H)` = 4.000000,
  `110-4(H)` = 4.000000,
  `114-4(H)` = 4.000000
  )
repeat_lengths <- ifelse(repeat_lengths < 1, 4, repeat_lengths)
```

>>>>

First we need to transform the data to something that is useable, aka a genclone
object. To avoid confustion with states, we are also transforming the two-letter
abbreviations for France, Mexico, and Australia to the full names.

```{r}
dat <- saj %>% 
  select(-(Isolate:Host)) %>% 
  df2genind(ind.names = saj$Isolate, 
            strata = select(saj, MCG:Host), # Filtering out severity and Isolate
            ploidy = 1) %>%
  as.genclone()
nameStrata(dat)[2] <- "Region"
pops <- levels(strata(dat)$Region)
levels(strata(dat)$Region) <- case_when(pops == "FR" ~ "France", 
                                        pops == "MX" ~ "Mexico", 
                                        pops == "AU" ~ "Australia", 
                                        TRUE ~ pops)
dat
locNames(dat)
```

### Gathering Repeat Lengths

The repeat lengths were contained in the `A1_Copy of binned-genotypes_SE.xlsx`
spreadsheet in the "replen est" sheet. Because this sheet contained several
merged cells and other oddities, I copy+pasted the relevant data here and 
parsed it from the text.

```{r}
rl <- read_tsv("dinuc			compound			hexinuc			dinuc			dinuc			dinuc			dinuc			trinuc			dinuc			compound			compound			tetranuc			dinuc			tetranuc			tetranuc			tetranuc
(GT)8			[(GT)2GAT]3(GT)14GAT(GT)5[GAT(GT)4]3(GAT)3			(TTTTTC)2(TTTTTG)2(TTTTTC)			(GA)14			(CA)12			(CA)9(CT)9			(CA)9			(TTA)9			(GT)7GG(GT)5			(CA)6(CGCA)2(CAT)2			(CA)7(TACA)2			(TACA)10			(CT)12			(CATA)25			(TATG)9			(AGAT)14(AAGC)4
 5-2(F)	bins	count	 5-3(F)	bins	count	 6-2(F)	bins	count	 7-2(F)	bins	count	 8-3(H)	bins	count	 9-2(F)	bins	count	 12-2(H)	bins	count	 17-3(H)	bins	count	 20-3(F)	bins	count	 36-4(F)	bins	count	 50-4(F)	bins	count	 55-4(F)	bins	count	 92-4(F)	bins	count	 106-4(H)	bins	count	110-4(H)	bins	count	114-4(H)")

x <- rl %>%
  select(-starts_with("X")) %>% # removing non-informative columns
  slice(-1) %>%                 # removing first row (repeat patterns)
  gather(replen, locus) %>%
  mutate(replen = strsplit(replen, "_") %>% map_chr(1)) %>% # fix duplicated column names
  mutate(replen = case_when(
    grepl("^di", .$replen)    ~ 2,
    grepl("^tri", .$replen)   ~ 3,
    grepl("^tetra", .$replen) ~ 4,
    grepl("^hex", .$replen)   ~ 6,
    TRUE                      ~ 0.5
  ))

x <- paste("c(", paste(paste0("`", x$locus, "`", " = ", x$replen), collapse = ",\n"), ")", sep = "\n")
cat(x)

repeat_lengths <- eval(parse(text = x))
repeat_lengths <- ifelse(repeat_lengths < 1, 4, repeat_lengths)
repeat_lengths
```
